Msc Thesis Figures

### 2020-08-20 docs/msc_thesis_figures.Rmd
udpate warning

```{r data_prep, message=FALSE, warning=TRUE, paged.print=TRUE}
# Results dir + mun shapefile
mun <- st_read("../data/mun/munic_SHP_clean.shp", quiet = TRUE)

>>>>

```{r data_prep, message=FALSE, warning=FALSE, paged.print=TRUE}
# Results dir + mun shapefile
mun <- st_read("../data/mun/munic_SHP_clean.shp", quiet = TRUE)
